Active-contours driven registration method for structure-informed segmentation of diffusion MR images

### 2015-04-07 Publications/2015-NeuroImage/04-methods.tex
edits received from Andres
final improvements before sending to authors, removed ANOVA

\begin{figure}
	\includegraphics[width=\linewidth]{figures/figure01}
	\caption{The active contours are defined as the interfacing surfaces of the competing
	  \glspl{roi} $\Omega_i$.
	They are represented in green and dark blue colors in this close-up.
	They iteratively evolve following their inner normals $\hat{n}_i$ at each vertex
	  $\vec{v}_i$ of the mesh.
	The gradient speeds $\bar{s}_i$ are computed as the disparity between data energies of
	  the vertex $\vec{v}_i$ in each limiting region (see \suppl{equation SM5})..
	In this figure, the gradient speed corresponding to $\vec{v}_1$ is written in the lower
	  box, $\Omega_{wm}$ being the inner limiting region and $\Omega_{gm}$ the outer, and
    $w_{0,1}$ the relative area associated to vertex $\vec{v}_1$ with respect to
    the total area of surface $\Gamma_0$.
	% Finally, every $\bar{s}_i$ is associated with the control points $\vec{u}_k$ through
	%   the corresponding weights $\psi_k(\vec{v}_i)$ by Eq. \eqref{eq:gradient_wshape}.
	}\label{fig:method}
\end{figure}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t + \vec{g}_k\} }%
                  {\mathcal{F}\{(\delta^{-1} + \boldsymbol{\alpha})\, I - \boldsymbol{\beta}\Delta\}} \right\}.
  \label{eq:update_equation}
  \end{align}

@@

\subsection{Evaluation protocol}\label{sec:evaluation_protocol}
In order to assess the performance of \emph{regseg}, we defined a general
  evaluation protocol:
1) Extraction of the set of undistorted surfaces $\gammaset_R$;
2) computation of a ground-truth field of displacements $U_{true}$ that is applied to
  generate warped images ($M$) to segment;
3) execution of \emph{regseg} with $\gammaset_R$ and the warped data as inputs; and
4) visual assessment and computation of error metrics.

@@

\begin{figure*}
\includegraphics[width=\linewidth]{figures/figure03}
\caption{Experimental workflow real data from the \acrfull*{hcp}.
  1) $\gammaset_R$ are extracted from the anatomical reference (\gls*{t1} image).
  2) To operate as ground truth, we generate a plausible-synthetic distortion $U_{true}$
    from the fieldmap using \eqref{eq:fieldmap}.
  3) The \gls*{dmri} data are warped using $U^{-1}_{true}$ to reproduce the effects of real
    susceptibility-derived distortions.
  Target diffusion scalars (\gls*{fa} and \gls*{adc}) are computed on the distorted data and
    stacked to feed the multivariate input required by our algorithm.
  4) \emph{Regseg} is run, obtaining a $U_{test} = \hat{U}_{true}$, the estimation of
    the ground-truth deformation.
  5) Results are visually and quantitatively evaluated.}\label{fig:evworkflows}
\end{figure*}

>>>>

\begin{figure}
	\includegraphics[width=\linewidth]{figures/figure01}
	\caption{The active contours are defined as the interfacing surfaces of the competing
	  \glspl{roi} $\Omega_i$.
	They are represented in green and dark blue colors in this close-up.
	They iteratively evolve following their inward normals $\hat{n}_i$ at each vertex
	  $\vec{v}_i$ of the mesh.
	The gradient speeds $\bar{s}_i$ drive registration, and are computed as the disparity of data
    energies with respect to the two limiting regions of $M(\vec{v}_i)$, the features of the image
    $M$ in the location of vertex $\vec{v}_i$ (see \suppl{equation SM5}).
	In this figure, $\bar{s}_1$ is written in the lower
	  box, with $\Omega_{wm}$ being the inner limiting region, $\Omega_{gm}$ the outer region, and
    $w_{0,1}$ the relative area associated to vertex $\vec{v}_1$ with respect to
    the total area of surface $\Gamma_0$.
	% Finally, every $\bar{s}_i$ is associated with the control points $\vec{u}_k$ through
	%   the corresponding weights $\psi_k(\vec{v}_i)$ by Eq. \eqref{eq:gradient_wshape}.
	}\label{fig:method}
\end{figure}

@@

  \begin{align}
  \vec{u}_k^{t+1} = \mathcal{F}^{-1}\left\{ \frac{\mathcal{F}\{\delta^{-1} \, \vec{u}_k^t - \vec{g}_k\} }%
                  {\mathcal{F}\{(\delta^{-1} + \boldsymbol{\alpha})\, I - \boldsymbol{\beta}\Delta\}} \right\},
  \label{eq:update_equation}
  \end{align}
  where $I$ denotes the identity operator.

@@

\subsection{Evaluation protocol}\label{sec:evaluation_protocol}
In order to assess the performance of \emph{regseg}, we defined a general
  evaluation protocol:
1) Extraction of the set of undistorted surfaces $\gammaset_R$;
2) computation of a ground-truth field of displacements $U_{true}$ that is applied to
  generate warped images ($M$) to segment;
3) execution of \emph{regseg} with $\gammaset_R$ and the warped data as inputs; and
4) visual assessment and computation of error metrics.
How this protocol is adapted to the simulated phantoms and real data is covered in the
  following sections.

@@

\begin{figure*}
\includegraphics[width=\linewidth]{figures/figure03}
\caption{Experimental workflow real data from the \acrfull*{hcp}.
  1) $\gammaset_R$ are extracted from the anatomical reference (\gls*{t1} image).
  2) To operate as ground truth, we generate a plausible-synthetic distortion $U_{true}$
    from the fieldmap using \eqref{eq:fieldmap}.
  3) The \gls*{dmri} data are warped using $U_{true}$ to reproduce the effects of real
    susceptibility-derived distortions.
  Target diffusion scalars (\gls*{fa} and \gls*{adc}) are computed on the distorted data and
    stacked to feed the multivariate input required by \emph{regseg}.
  4) the method is run, obtaining a $U_{test} = \hat{U}_{true}$, the estimation of
    the ground-truth deformation.
  5) Results are visually and quantitatively evaluated.}\label{fig:evworkflows}
\end{figure*}

### 2015-04-07 Publications/2015-NeuroImage/05-results.tex
final improvements before sending to authors, removed ANOVA

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-b}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L-shape'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

\begin{table}
		\centering
		\footnotesize
    \begin{tabular}{lccccc}
    Res. & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    Low  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    High & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    \hline
    \end{tabular}
    \caption{95\% Confidence Intervals (CIs) were computed using bootstrapping of $10^4$ samples,
      for each phantom type and resolution.
    Taking into account the non-normal distribution of errors, we used the median as location
  		statistic.
    All the CIs were below the corresponding half-voxel size in all the phantom types.}\label{tab:ci_phantom}
\end{table}

\subsection{Evaluation on real datasets and cross-comparison}\label{sec:results_hcp}
%
Finally, we compared the performance of \emph{regseg} and the standard \gls*{t2b}
  registration.
We computed the \gls*{swindex} \eqref{eq:swindex} of every surface after registration,
  for both \emph{regseg} and the \gls*{t2b} methods.
Finally, to statistically compare the results, we performed a one-way ANOVA test
  on the warping indices for three specific surfaces of interest
  ($\Gamma_{VdGM}$, $\Gamma_{WM}$, and $\Gamma_{pial}$).
These interfaces are critical in analyses of whole-brain tractography.
The one-way ANOVA evidenced that error distributions were significantly different,
  $p \approx 2 \times 10^{-9}$.
We also reported the 95\% CIs of the \gls*{swindex} for those surfaces.
The aggregate CI for \emph{regseg} was 1.08 - 1.50 [mm], whereas the \gls*{t2b} method
  yielded an aggregate CI of 2.06 - 2.43 [mm].
The quantitative results of the ANOVA tests and the CIs are presented in \autoref{tab:results_real}.
Visual assessment of the 16 cases is included in the \suppl{section S5}.
In \autoref{fig:results_real}, box A, the visual report for one subject is supplied.
Box B presents the corresponding violin plots of error distributions by registration method
  and surface.

\begin{table}
		\centering
		\footnotesize
		\tabcolsep=0.05cm
    \begin{tabular}{cccccc}
    & & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ & Aggregate \\
    \hline
    \multirow{2}{*}{CI}
       & \emph{regseg}        & 0.50 - 0.78 & 0.50 - 0.55 & 0.66 - 0.73 & 0.56 - 0.66 \\
       & T2B                  & 1.78 - 2.58 & 1.94 - 2.36 & 2.16 - 2.58 & 2.05 - 2.39 \\
    \hline
    \multirow{2}{*}{ANOVA}
       & p-value  & 1.5$\times$10$^{-8}$& 6.3$\times$10$^{-16}$& 4.2$\times$10$^{-16}$ & 4$\times$10$^{-34}$ \\
       & f-stat   & 60.03               & 255.82               & 263.97                & 377.82              \\
    \hline
    \end{tabular}
    \caption{All the 95\% CIs of the \gls*{swindex} distributions computed for the
      surfaces of interest were lower for \emph{regseg} with respect to the competing
      method.
    CIs reported in this table were computed using bootstrapping with mean as location
      statistic and $10^4$ samples.
    One-way-ANOVA tests indicated that there is a significant difference between our method and
      the competing method of choice.
    }\label{tab:results_real}
\end{table}

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-a}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-b}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{The evaluation instrument automatically renders the overlay between the
	  target \gls*{fa} image and the resulting contours after distortion estimation (yellow color) and
	  their theoretical location using the ground-truth (green color).
	The first two rows show several axial slices for \emph{regseg} (``proposed'' row) and the
	  competing method.
	The last two rows represent the sagittal view.
	We intentionally omitted the coronal slicing as it is the least informative, given the directional property
	  of distortions.
	Red arrows point to regions where the accuracy of the proposed method more clearly overperformed
	  the competing method.
	}\label{fig:results_real}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-b}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

\begin{table}
		\centering
		\footnotesize
    \tabcolsep=0.1cm
    \begin{tabular}{lccccc}
    Res.   & ``gyrus'' & ``ball''  & ``box''   & ``L''     & Aggreg.    \\\hline
    1.0mm  & 0.18-0.38 & 0.31-0.45 & 0.34-0.42 & 0.34-0.40 & 0.34-0.38  \\
    2.0mm  & 0.59-0.60 & 0.65-0.76 & 0.68-0.71 & 0.67-0.77 & 0.64-0.66  \\
    \hline
    \end{tabular}
    \caption{The vertex-wise Haussdorf distance between the ground-truth surfaces and their
    corresponding estimation with \emph{regseg} presented distributions with 95\% CI below
    the half-voxel size in all the phantom types.
    CIs were computed using bootstrapping of 10$^4$ samples, and median as location statistic.}\label{tab:ci_phantom}
\end{table}

\subsection{Evaluation on real datasets and cross-comparison}\label{sec:results_hcp}
%
Finally, we compared the performance of \emph{regseg} and the standard \gls*{t2b}
  method.
Visual assessment of the 16 cases is included in the \suppl{section S5}.
In \autoref{fig:results_real}, box A, the visual report for one subject is supplied.
We computed the \gls*{swindex} \eqref{eq:swindex} of every surface after registration,
  for both \emph{regseg} and the \gls*{t2b} methods.
Finally, to statistically compare the results, we performed Kruskal-Wallis H-tests
  (a non-parametric alternative to ANOVA) on the warping indices for three specific 
  surfaces of interest selected in \autoref{sec:experiments_evaluation}.
All the statistical tests evidenced that error distributions obtained with \emph{regseg} and
  the \gls*{t2b} were significantly different, and using the violin plots in box B of
  \autoref{fig:results_real} we observed that errors are always larger for \gls*{t2b}.
We also reported the 95\% CIs of the \gls*{swindex} for those surfaces.
The aggregate CI for \emph{regseg} was 1.08 - 1.50 [mm], whereas the \gls*{t2b} method
  yielded an aggregate CI of 2.06 - 2.43 [mm].
The results of the statistical tests and the CIs are summarized in \autoref{tab:results_real}.

\begin{table}
		\centering
		\footnotesize
		\tabcolsep=0.08cm
    \begin{tabular}{cccccc}
    & & $\Gamma_{VdGM}$  & $\Gamma_{WM}$ & $\Gamma_{pial}$ & Aggregate \\
    \hline
    \multirow{2}{*}{CI}
       & \emph{regseg}        & 0.50 - 0.78 & 0.50 - 0.55 & 0.66 - 0.73 & 0.56 - 0.66 \\
       & T2B                  & 1.78 - 2.58 & 1.94 - 2.36 & 2.16 - 2.58 & 2.05 - 2.39 \\
    \hline
    \multirow{2}{*}{H-tests}
       & p-value  & 4.1$\times$10$^{-6}$& 2.3$\times$10$^{-6}$& 2.3$\times$10$^{-6}$ & 1.8$\times$10$^{-16}$ \\
       & H-stat   & 21.20               & 22.31               & 22.31                & 67.85              \\
    \hline
    \end{tabular}
    \caption{The statistical analysis of results on real data supported that \emph{regseg} overperformed
    the alternative \acrfull{t2b} method.
    The distribution of errors computed for the surfaces of interest ($\Gamma_{VdGM}$, $\Gamma_{WM}$, $\Gamma_{pial}$)
      and the aggregate of all surfaces presented lower 95\% CIs for \emph{regseg}.
    CIs reported in this table were computed using bootstrapping with mean as location statistic and 10$^4$ samples.
    The Kruskal-Wallis H-tests indicated that there is a significant difference between \emph{regseg} and
      the \gls*{t2b} method.
    }\label{tab:results_real}
\end{table}

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-a}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figures/figure05-b}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figures/figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{A. Example of one report for visual assessment, automatically generated by the evaluation instrument.
    Each view shows one component of the input image (in this case, the \gls*{fa} map), the ground-truth location
    of the surfaces (green contours), and the resulting surfaces with the method under test (yellow contours).
  First two rows show axial slices for \emph{regseg} and the \acrfull*{t2b} method, and the last two rows
    show corresponding sagittal views.
  Coronal view is omitted since it is the least informative due to the the directional property
    of distortions.
	Red arrows point to regions where \emph{regseg} overperformed the \gls*{t2b} method.
  B. Violin plots of error distributions of each surface, with indication of the voxel size of the \gls*{dmri} images
    (1.25 mm), and supporting the improved results of \emph{regseg} in the proposed settings.
	}\label{fig:results_real}
\end{figure*}

### 2015-04-07 Publications/2015-NeuroImage/06-discussion.tex
final improvements before sending to authors, removed ANOVA

We evaluated \emph{regseg} in a real environment, using the experimental framework presented
  in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database with both \emph{regseg}
  and an in-house replication of the \gls*{t2b} correction method.
\emph{Regseg} showed very high accuracy, with an aggregate 95\% \gls*{ci} of 0.56-0.66 [mm],
  bellow the pixel size of 1.25mm.
The misregistration error remaining after \emph{regseg} was significantly lower ($p < 0.01$) than the
  error corresponding to the \gls*{t2b} correction, using the one-way ANOVA test
  (\autoref{tab:results_real}).
Visual inspection of all the results (\suppl{section S5}) and the violin plots included in
  \autoref{fig:results_real} confirmed that \emph{regseg} overperformed the \gls*{t2b} method
  in our settings.
Even though we carefully configured the \gls*{t2b} method by using the same algorithm and
  same settings of a widely used software, cross-comparison experiments are prone to
  the so-called \emph{instrumentation bias} \citep{tustison_instrumentation_2013}.
Therefore, these results do not prove that the \emph{regseg} software \emph{is better than} the
  \gls*{t2b} method.
The results reported let us propose \emph{regseg} as a solid option in the application field.
Additionally, the \gls*{t2b} may introduce an additional (and small) error in the necessary
  registration of \gls*{t2} to \gls*{t1} space.

>>>>

We evaluated \emph{regseg} in a real environment, using the experimental framework presented
  in \autoref{fig:evworkflows}.
We processed 16 subjects from the \gls*{hcp} database with both \emph{regseg}
  and an in-house replication of the \gls*{t2b} correction method.
\emph{Regseg} showed very high accuracy, with an aggregate 95\% \gls*{ci} of 0.56-0.66 [mm],
  bellow the pixel size of 1.25mm.
The misregistration error remaining after \emph{regseg} was significantly lower ($p < 0.01$) than the
  error corresponding to the \gls*{t2b} correction, using Kruskal-Wallis H-tests
  (\autoref{tab:results_real}).
Visual inspection of all the results (\suppl{section S5}) and the violin plots included in
  \autoref{fig:results_real} confirmed that \emph{regseg} overperformed the \gls*{t2b} method
  in our settings.
Even though we carefully configured the \gls*{t2b} method by using the same algorithm and
  same settings of a widely used software, cross-comparison experiments are prone to
  the so-called \emph{instrumentation bias} \citep{tustison_instrumentation_2013}.
Therefore, these results do not prove that the \emph{regseg} software \emph{is better than} the
  \gls*{t2b} method.
The results reported let us propose \emph{regseg} as a solid option in the application field.
Additionally, the \gls*{t2b} may introduce an additional (and small) error in the necessary
  registration of \gls*{t2} to \gls*{t1} space.
